Exposing and Exploring Disputed Statements on the Web

### 2009-03-30 papers/uist_thinklink/thinklink.tex

\title{Exposing Disputed Statements on the Web}

@@

\abstract
Think Link is a tool that helps users know when information they read on a the web is disputed. As a user browses the web, Think Link highlights snippets of text that make claims that users have identified as being disputed. If a user clicks on a highlighted snippet, Think Link will display an argument graph showing the best evidence for and against the claim the snippet is making.

Users provide all of Think Link's information: they create new claims, mark new snippets, connect snippets to claims, and vote for the best evidence.
Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources tha tpresent alternative viewpoints.

@@

In this paper we present Think Link, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view. If a user has installed the Think Link browser extension hen it will highlight snippets of text on the web that make disputed claims (Figure~\ref{highlight}). When a user clicks on a highlighted snippet, Think Link presents them with an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).

@@

\item[Sceptical Readers] want to know when information they read is disputed so that they can avoid being misled. They install Think Link as a browser plugin so that it will highlight disputed claims and show them opposing points of view.
\end{description}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=5cm]{../screenshots/v2_popup_dim.png}
	\caption{Click on a snippet to investigate evidence for the claim it makes}
	\label{claimview}
	\end{center}
\end{figure}

@@

The design of Think Link was guided by two user studies in which we observed users' behaviour as they perfomed tasks fitting the usage scenarios for Activist and Sceptical Reader.

@@

Think Link builds on prior work in several different areas. The argument graph is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. The idea of highlighting potentially unstrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information. Think Link's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.

@@

Cohere~\cite{Shum2008} allows a user to specify one or more related URLs when creating a new claim, and provides a Firefox plugin to help a user create a claim about a web page they are reading. Unlike Think Link, Cohere is not designed to be used to alert users about disputed snippets. Cohere works with URLs rather than snippets and does not allow one to connect a new URL to an existing claim created by someone else.

Although Think Link's argument graph is similar to that used by IBIS tools, it uses it for a different purpose. In Think Link the focus is on snippets, and the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim. A user is expected to create a new claim only when they want to group together several snippets that make that claim. A Think Link user is expected to form an opinion primarily by looking at the snippets and the pages they are part of, rather than by looking at the argument graph itself. By contrast, in an IBIS tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph. A gIBIS user is encouraged to break their argument down into as many separate ideas as possible and is expected to use the graph itself to reach a conclusion. In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims but is associated with many snippets.

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners investigated to determine whether they are true. 
Think Link's database automatically imports all contentious claims identified by Snopes.
FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. We use Fact Check as a useful source of disputed claims.

@@

Videolyzer~\cite{Diakopoulos2008}\footnote{http:\\www.videolyzer.com} allows users to annotate and comment on political videos. A user can attach a comment to a section of video and tag it for bias, accuracy, or rhetorical technique. Comments can include references to external sources that back up the argument being made. Like SpinSpotter, Videolyzer does not attempty to gather multiple video sections that make a common contentious claim.

@@

The panel for a claim (Figure~\ref{panel}) lists evidence that will help a user decide whether the claim is true. Evidence is categorized as either supporting, opposing, or being related-to the claim. The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument. Evidence can either be a snippet that talks about that claim, or another claim whose truth would support or oppose this claim.  The panel for a snippet shows the snippet text in the context of the web page it is part of. This, combined with the cascading panel interface allows a user to quickly read the evidence for and against a claim without having to leave the claim browser interface.

\todo{Remove ``related`` fom the topics list - confuses with related claims}
\todo{Show the other panels?}

@@

Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of node: snippets, claims, and topics. A snippet is a region of text taken from a web page; a claim is a statement about the world or a position that one can take on some issue; and a topic is an issue that a claim might address or a thing that a claim might be about. Nodes are connected together by typed, directed, links. There are three link types: supports, opposes, and relates-to. A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.

@@

Think Link's graph model is a simpler than that used by gIBIS~\cite{Conklin1987}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to relation. While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Think Link's is designed for, and we have found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.

The order in which evidence is displayed is determined by user voting. A user can vote for or against a particular piece of evidence by clicking on the voting buttons next to that item~(Figure~\ref{voting}). When a user votes for something it will be moved to the top of their list, and also make that item earlier for other users.

One danger in a voting system is that a large group of people may drown out the opinions of their opponents by voting down their opinions. Think Link uses several strategies to try to avoid this happening. Firstly, positive votes count for more than negative votes. Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent. Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side. In some cases, it may still be necessary to introduce a moderation system similar to that used in Wikipedia, where trusted users can override popular opinion when things go wrong.

@@

@@

Think Link does not require a user to specify the disputed claim a snippet is making at the point at which they mark it. Instead, Think Link encourages a user to gather many snippets and then use the claim browser interface to associate claims with snippets in bulk.
One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagree with. 
In this case, the user can save time by first collecting all their snippets, and then attaching all their snippets to their disputed claim together.

@@

Think Link uses the same suggestion system to suggest connections between claims. It is important to make sure that the argument graph stays well connected as it grows. If users create duplicate claims or don't connect their claims to existing claims then then graph becomes less useful. Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to create a suggested connection with a single click.

@@

Even though Think Link tries to make creating and linking snippets as easy as possible, it still requires a non-trivial amount of work. Fortunately, several activist users we talked to told us that they already spend a lot of time performing similar tasks; currently they search for web pages about issues they care about and respond to disputed claims by posting comments or talking about them on their own blog. Some users use tools like Google Alerts\footnote{http://www.google.com/alerts} to learn when a new page appears about an issue they are interested in. Moreover, although it would not be practical for activists to mark up all pages on the web, web page popularity follows a Zipf law~\cite{Krashkov2006}, and so one can achieve useful coverage by only marking up the relatively small number of very popular pages (for example major news sites).

@@

The page annotation script is a javascript file that can be included into any HTML page. When it is run on a page it sends the page URL to the server, asking it to send back any snippets on that page. There are of course privacy issues here since this could allow user browsing to be tracked. We reduce this problem a little by not sending cookies or other identifying information, and making the protocol cacheable. In future we hope to device a way to reduce concerns further. One idea we are exploring is to use hashing similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/} to identify pages that might contain disputed information and then requiring a user to explicitly enable Think Link for particular sites for Think Link will request disputed snippets.

@@

For the first study we recruited twelve paid participants, five female, seven male, aged 18 to 52. Nine participants maintained a blog. We recruited participants by posting an advert on Craigslist\footnote{http://craigslist.org}.
Our intention was to recruit users who fit our ``sceptical reader'' and ``activist'' personas. In our advert, we asked people to tell us what kind of information they looked at on the web and how they shared information with others. We selected participants who looked at information that was likely to be disputed (e.g. political commentry) and who said they regularly shared information with friends.

@@

Study sessions took approximately fourty five minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension. We first demonstrated Think Link's interface, and then asked them to find information as they would normally and use Think Link to mark snippets that made claims that they thought were interesting or disputed. For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.

@@

% \subsubsection{High-Level Impressions}

%\todo{Do we want this section}
% 
% Response was generally positive, with many participants being very keen to use the tool soon. One participant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed. Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.
% 
% Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader). One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''. A smaller number said they would want to mark up claims they disagreed with (activist). One participant who was a political blogger was very excited about the ability to mark up things he thought were lies.
% 
% Most participants in the first study, and all participants in the second study were able to use the tool competently. Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. One participants said they found the tool ``very intuitive''.

@@

Since a user was required to enter a claim whenever they created a snippet, there was an incentive for the user to enter a claim as quickly as possible so they they could make the dialog go away. Several users created a new claim that was equivalent to a claim that already existed, and several users repeatedly created a claim that had the exact same text as the snippet. The final interface reduces this problem by not requiring a user to associate a claim with a snippet until they decide that this is something that they want to do, and they have a particular disputed claim in mind.

@@

The prototype versions of Think Link used a drag-and-drop interface to allow a user to create links between claims. In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find others claims and then drag them into appropriate positions in the argument graph. The second interface (Figure~\ref{secondbrowser}) followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between. 
In both cases, we found that users would often not realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}). We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and the rendering of a claim did not have any visual clue to suggest that they could use drag and drop to create connections. In the final interface we resolved this issue by moving to a ``click to link'' interface and having the connection actions (``add claim'' etc) prominently visible.

>>>>

\title{Exposing and Exploring Disputed Statements on the Web}

@@

\abstract
Think Link is a tool that helps users know when information they read on the web is disputed. 
As a user browses the web, Think Link highlights snippets of text that make claims that users have identified as contentious. 
If a user clicks on a highlighted snippet, Think Link displays an argument graph showing the best evidence for and against the claim the snippet is making.

Users provide all of Think Link's information: they create new claims, mark new snippets, connect snippets to claims, and vote for the best evidence.
Think Link is designed to support two primary usage scenarios: (i) Activists care strongly about a particular issue and combine Think Link with a search engine to find and mark snippets that make claims that they disagree with; and (ii) Sceptical Readers install Think Link as a browser extension to see when statements they read are disputed and find other sources that present alternative viewpoints.

@@

In this paper we present Think Link, a tool that helps users discover when information they read is disputed, and helps users find sources with alternative points of view. 
If a user has installed the Think Link browser extension then it will highlight snippets of text on the web that make disputed claims (Figure~\ref{highlight}). 
When a user clicks on a highlighted snippet, Think Link presents an argument graph that shows the best evidence for and against the claim (Figure~\ref{claimview}).

@@

\item[Sceptical Readers] want to know when information they read is disputed so that they can avoid being misled. They install Think Link as a browser extension so that it will highlight disputed claims and show them opposing points of view.
\end{description}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/v2_popup_dim.png}
	\caption{Click on a snippet to investigate evidence for the claim it makes}
	\label{claimview}
	\end{center}
\end{figure}

@@

Think Link's design was guided by two user studies in which we observed users' behavior as they performed tasks fitting the usage scenarios for Activist and Sceptical Reader.

@@

Think Link builds on prior work in several different areas. The argument graph is influenced by IBIS~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}. 
The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Think Link uses the community to collect and filter information. Think Link's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}.

@@

Cohere~\cite{Shum2008} allows a user to specify one or more related URLs when creating a new claim, and provides a Firefox extension to help a user create a claim about a web page they are reading. Unlike Think Link, Cohere is not designed to be used to alert users about disputed snippets. Cohere works with URLs rather than snippets and does not allow one to connect a new URL to an existing claim created by someone else.

Although Think Link's argument graph is similar to that used by IBIS tools, it is used for a different purpose. 
In Think Link the focus is on snippets; the argument graph is used to organize snippets, identify when snippets are disputed, and identify which snippets provide the best evidence for a particular claim. 
A user is expected to create a new claim only when they want to group together several snippets that make that claim. 
A Think Link user is expected to form an opinion primarily by looking at the snippets and the pages in which they appear, rather than by looking at the argument graph itself. By contrast, in an IBIS tool such as gIBIS~\cite{Conklin1987a}, the focus is on the argument graph. A gIBIS user is encouraged to break their argument down into as many separate ideas as possible and is expected to use the graph itself to reach a conclusion. In Think Link it is perfectly acceptable to have a claim that is not linked to any other claims but is associated with many snippets.

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners investigated to determine whether they are true. 
Think Link's database automatically imports all contentious claims identified by Snopes.
FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. 
%We use Fact Check as a useful source of disputed claims.

@@

Videolyzer~\cite{Diakopoulos2008}\footnote{http:\\www.videolyzer.com} allows users to annotate and comment on political videos. A user can attach a comment to a section of video and tag it for bias, accuracy, or rhetorical technique. Comments can include references to external sources that back up the argument being made. Like SpinSpotter, Videolyzer does not attempt to gather multiple video sections that make a common contentious claim.

@@

The panel for a claim (Figure~\ref{panel}) lists evidence that will help inform the users opinion about the claim and alternative points of view. Evidence is categorized as either supporting, opposing, or being related-to the claim. The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument. Evidence can either be a snippet that talks about that claim, or another claim whose truth would support or oppose this claim.  The panel for a snippet shows the snippet text in the context of the web page it is part of. This, combined with the cascading panel interface allows a user to quickly read the evidence for and against a claim without having to leave the claim browser interface.

\todo{Remove ``related`` from the topics list - confuses with related claims}
\todo{Show the other panels?}

@@

Think Link's claim graph is a variant of the IBIS~\cite{Rittel1973} model. There are three types of nodes: snippets, claims, and topics. 
A snippet is a region of text taken from a web page; a claim is a statement about the world or a position that one can take on some issue; and a topic is an issue that a claim might address or a thing that a claim might be about. Nodes are connected together by typed, directed, links. 
There are three link types: supports, opposes, and relates-to. A snippet or claim can support, oppose, or relate-to a claim; and any node can relate-to a topic.

@@

Think Link's graph model is simpler than that used by gIBIS~\cite{Conklin1987a}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to relation. 
While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Think Link is designed for. 
We have also found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.

The order in which evidence is displayed is determined by user voting. A user can vote for or against a particular piece of evidence by clicking on the voting buttons next to that item~(Figure~\ref{voting}). When a user votes for something it will be moved to the top of their list, and also make that item appear earlier for other users.

One danger in a voting system is that a large group of people may drown out the opinions of their opponents by voting down their opinions. Think Link uses several strategies to try to avoid this happening. Firstly, positive votes count for more than negative votes. Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent. Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side. In some cases, it may still be necessary to introduce a moderation system similar to that used in Wikipedia, where trusted users can override popular opinion when things go wrong. 
\todo{Talk about whether we know if this works}

@@

The only difference between selecting ``this is disputed'' and ``this is interesting'' is that Think Link remembers which you used when you marked a snippet. A snippet is only highlighted in red for other users if it is connected to a disputed claim. The main reason for having two different options is to show users what kinds of information Think Link expects them to mark as snippets.
\todo{Say something smart about the difference}

@@

Think Link does not require a user to specify the claim a snippet is making at the point at which they mark it. Instead, Think Link encourages a user to gather many snippets and then use the claim browser interface to associate claims with snippets in bulk.
One anticipated usage scenario for Think Link is an activist user who uses a search engine to find a large number of snippets that make a claim that they disagree with. 
In this case, the user can save time by first collecting all their snippets, and then attaching all the snippets to their disputed claim at the same time.

@@

Think Link uses the same suggestion system to suggest connections between claims. It is important to make sure that the argument graph stays well connected as it grows. If users create duplicate claims or don't connect their claims to existing claims then the graph becomes less useful. Think Link tries to make it easy for users to keep the claim graph well connected by suggesting claims that should be linked together and allowing a user to create a suggested connection with a single click.

@@

Even though Think Link tries to make creating and linking snippets as easy as possible, it still requires a non-trivial amount of work. Fortunately, several activist users we talked to told us that they already spend a lot of time performing similar tasks: currently they search for web pages about issues they care about and respond to disputed claims by posting comments or talking about them on their own blog. Some users use tools like Google Alerts\footnote{http://www.google.com/alerts} to learn when a new page appears about an issue they are interested in. Moreover, although it would not be practical for activists to mark up all pages on the web, web page popularity follows a Zipf law~\cite{Krashakov2006}, and so one can achieve useful coverage by only marking up the relatively small number of very popular pages (for example major news sites).

@@

The page annotation script is a javascript file that can be included into any HTML page. When it is run on a page it sends the page URL to the server, asking it to send back any snippets on that page. There are of course privacy issues here since this could allow user browsing to be tracked. We lessen this problem by not sending cookies or other identifying information, and making the protocol cacheable. 
In the future we hope to devise a way to reduce concerns further. 
One idea we are exploring is to use hashing similar to that used by Google Safe Browsing\footnote{http://code.google.com/p/google-safe-browsing/} to identify pages that might contain disputed information and require a user to explicitly ask for Think Link to highlight snippets on a particular site.

@@

For the first study we recruited twelve paid participants, five female, seven male, aged 18 to 52. Nine participants maintained a blog. We recruited participants by posting an advert on Craigslist\footnote{http://craigslist.org}.
Our intention was to recruit users who fit our ``sceptical reader'' and ``activist'' personas. In our advert, we asked people to tell us what kind of information they looked at on the web and how they shared information with others. We selected participants who looked at information that was likely to be disputed (e.g. political commentary) and who said they regularly shared information with friends.

@@

Study sessions took approximately forty five minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link extension. We first demonstrated Think Link's interface, and then asked them to find information as they would normally and use Think Link to mark snippets that made claims that they thought were interesting or disputed. For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.

@@

\subsubsection{High-Level Impressions}

Response was generally positive, with many participants being very keen to use the tool soon. One participant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed. Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.

Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader). One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''. A smaller number said they would want to mark up claims they disagreed with (activist). One participant who was a political blogger was very excited about the ability to mark up things he thought were lies.

Most participants in the first study, and all participants in the second study were able to use the tool competently. Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. Participants said they found the tool ``very intuitive'' and ``really cool''.

@@

Since a user was required to enter a claim whenever they created a snippet, there was an incentive for the user to enter a claim as quickly as possible so they could make the dialog go away. 
Several users created a new claim that was equivalent to a claim that already existed, and several users repeatedly created a claim that had the exact same text as the snippet. The final interface reduces this problem by not requiring a user to associate a claim with a snippet until they decide that this is something that they want to do, and have a particular disputed claim in mind.

@@

The prototype versions of Think Link used a drag-and-drop interface to allow a user to create links between claims. In the first interface (Figure~\ref{oldbrowser}) a user could use a search box to find others' claims and then drag them into appropriate positions in the argument graph. The second interface (Figure~\ref{secondbrowser}) followed a file-manager metaphor, providing two identical browser windows that a user could drag and drop claims between. 
In both cases, we found that users would often not realize they could use drag and drop to organize claims, even when we added a prominent information message at the top of the display (Figure~\ref{secondbrowser}). We believe that part of the problem was that users are not used to using drag-and-drop in a web interface, and the rendering of a claim did not have any visual clue to suggest that they could use drag and drop to create connections. In the final interface we resolved this issue by moving to a ``click to link'' interface and having the connection actions (``add claim'' etc) prominently visible.
